A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-14 tex/codatadp.tex
more data

\begin{abstract}
Codatatypes naturally capture potentially infinite data structures and
processes. We present a decision procedure that combines reasoning about
datatypes and codatatypes. The dual of the cyclicity rule for datatypes is a
bisimilarity rule that identifies equal values, also in the presence of cyclic
($\omega$-regular) data. The procedure is complete for ground problems and is
composable via the Nelson--Oppen method. It has been implemented in the latest
version of CVC4, a state-of-the-art SMT solver. An evaluation based on
problems generated from Isabelle theories demonstrates the potential of the
procedure.
\end{abstract}

@@

                 Datatype suite     Mixed suite        Codatatype suite
                (2345 problems)    (XXX problems)       (1240 problems)

   w/o (co)data        800           1255                699
   w data              815           1268                
   w codata                          1270                712
   w both                            1273
\end{verbatim}}

>>>>

\begin{abstract}
Codatatypes naturally capture potentially infinite data structures and
processes. We present a decision procedure that combines reasoning about
datatypes and codatatypes. The dual of the cyclicity rule for datatypes is a
bisimilarity rule that identifies equal values, also in the presence of cyclic
($\omega$-regular) data. The procedure is complete for ground and universal
problems and is composable via the Nelson--Oppen method. It has been
implemented in the latest version of CVC4, a state-of-the-art SMT solver. An
evaluation based on problems generated from Isabelle theories demonstrates the
potential of the procedure.
\end{abstract}

@@

                 Codatatype suite     Mixed suite        Datatype suite
                (2345 problems)    (XXX problems)       (1240 problems)

   w/o (co)data        800           1122                699
   w codata            815 (2)       1139 (3)
   w data                            1153 (6)            712 (4)
   w both                            1170 (3+6)
\end{verbatim}}
